r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2021-01-18 r-package/paper2020/paper2020.Rmd
add Matt as co-author. Change abstract

---
title: 'r5r: rapid realistic routing on multimodal transport networks with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga"
date: "`r Sys.Date()`"
output:
   html_document: default
   word_document: default
   pdf_document: default
abstract: Routing is a key step in transport planning. Nonetheless, researchers and practitioners face challenges to perform this task, such as the costs of licensed software and long computation times. Conveyal’s R<sup>5</sup> is a multimodal transport network router that offers meaningful planning features, such as calculating travel times over a time window and returning multiple itineraries for a single or multiple origin/destination pairs. This paper describes r5r, an open source R package that leverages on R<sup>5</sup> to allow users to efficiently compute travel time matrices and generate detailed itineraries between a set of origins and destinations at no expense.
urlcolor: blue
bibliography: references.json
---

@@

The `travel_time_matrix()` function takes, as inputs, the spatial location of origins/destinations  (either as a spatial `sf POINT` object, or as a `data.frame` containing the columns `id`, `lon` and `lat`) and a few travel parameters such as _maximum trip duration_ or _walking distance_, and outputs travel time estimates for each origin-destination pair at a set `departure_datetime`.

@@

<!-- If the destination points cover the entire study area, the output can easily be used to build ishochrone-like visualizations.  -->
In our example, we can visualize the isochrone departing from the central bus station as follows:

@@

<!-- old isochrone code
# ```{r}
# cutoffs <- seq(0, 120, 20)
# 
# # select the travel time matrix departing from a given origin
# central_bus_stn <- points[291,]
# ttm_iso <- ttm[fromId %in% central_bus_stn$id ] 
# 
# # aggregate travel-times
# ttm_iso[, isochrones := cut(x=travel_time_p099, breaks=cutoffs), by= fromId]
#   
# # join travel-matrix results to points
# ttm_iso[points, on=c('toId' ='id'), `:=`(lon = i.lon, lat = i.lat)]
# 
# ggplot(ttm_iso, aes(x=lon, y=lat, colour = isochrones)) +
#    geom_point(size = 2) +
#    geom_point(data = central_bus_stn, aes(x=lon, y=lat), colour="blue", size = 2) +
#    coord_map() +
#    scale_colour_brewer(palette = "Reds") +
#    facet_wrap(~fromId) +
#    theme_minimal() +
#    theme(axis.title = element_blank(),
#          panel.border = element_rect(fill = NA, colour = "grey40"))
# ```
 -->

>>>>

---
title: 'r5r: rapid realistic routing on multimodal transport networks with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga, Matthew Wigginton Conway"
date: "`r Sys.Date()`"
output:
   html_document: default
   word_document: default
   pdf_document: default
abstract: Routing is a key step in transport planning and research. Nonetheless, researchers and practitioners often face challenges to perform this task due to the cost of licensed software and long computation times. Conveyal’s R<sup>5</sup> is a multimodal transport network router that offers multiple planning features, such as calculating travel times over a time window, and returning multiple itineraries for origin/destination pairs. This paper describes r5r, an open-source R package that leverages on R<sup>5</sup> to allow users to efficiently compute travel time matrices and generate detailed itineraries between sets of origins and destinations at no expense using seamless parallel computing.
urlcolor: blue
bibliography: references.json
---

@@

The `travel_time_matrix()` function takes, as inputs, the spatial location of origins/destinations (either as a spatial `sf POINT` object, or as a `data.frame` containing the columns `id`, `lon` and `lat`) and a few travel parameters such as *maximum trip duration* or *walking distance*, and outputs travel time estimates for each origin-destination pair at a set `departure_datetime`.

@@

<!-- If the destination points cover the entire study area, the output can easily be used to build ishochrone-like visualizations.  -->

In our example, we can visualize the isochrone departing from the central bus station as follows:

@@

```{=html}
<!-- old isochrone code
# ```{r}
# cutoffs <- seq(0, 120, 20)
# 
# # select the travel time matrix departing from a given origin
# central_bus_stn <- points[291,]
# ttm_iso <- ttm[fromId %in% central_bus_stn$id ] 
# 
# # aggregate travel-times
# ttm_iso[, isochrones := cut(x=travel_time_p099, breaks=cutoffs), by= fromId]
#   
# # join travel-matrix results to points
# ttm_iso[points, on=c('toId' ='id'), `:=`(lon = i.lon, lat = i.lat)]
# 
# ggplot(ttm_iso, aes(x=lon, y=lat, colour = isochrones)) +
#    geom_point(size = 2) +
#    geom_point(data = central_bus_stn, aes(x=lon, y=lat), colour="blue", size = 2) +
#    coord_map() +
#    scale_colour_brewer(palette = "Reds") +
#    facet_wrap(~fromId) +
#    theme_minimal() +
#    theme(axis.title = element_blank(),
#          panel.border = element_rect(fill = NA, colour = "grey40"))
# ```
 -->
```
